Effects of bulk gas rotation on the emergent Lyman-$\alpha$ line in distant galaxies

### 2013-02-22 paper/Analisis.tex
more text and fits table

If we now study the effect of the optical depth $\tau$ in the maxima position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the optical depth increase (include reference of previous articles) the maxima position increase and this is a well known result, but when rotation is included the dependence is not linear.
%(think a lit bit more on this, maybe make a regression)
%explain the method to find the maxima position

\subsection{Line Width}
\label{sec:LW}

Another effect that the rotation of the gas produce is in the  width
of the lyman alpha line. The width of the line provide information of
how many photons scape with a particular wave lenght, in the
ideal case in which all the photons scape with the same wave lenght
the outcoming spectrum would be narrower. For all the models we study we
found that as the rotational velocity increase the line width
increase this is show in Fig.[4].\\

@@

We also found that the width for a particular model is not the same
for differents angles of observation in particular as the angle
increase the width also increase, it means that as the angle increase
the number of scatterings of the photons increasse for this reason we
see a broader line. Fig.[5]\\

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
\caption{Width variation in function of theta}
\end{center}
\end{figure}

@@

\section{Observational implications}

>>>>

If we now study the effect of the optical depth $\tau$ in the maxima position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the optical depth increase (include reference of previous articles) the maxima position increase and this is a well known result, but when rotation is included the dependence is not linear.
%(think a lit bit more on this, maybe make a regression)
%explain the method to find the maxima position
% Nscatt plots should give a hint about central maxima.
\subsection{Line Equivalent Width}
\label{sec:LW}

The width of the line provide information of
how many photons scape with a particular wave lenght, in the
ideal case in which all the photons scape with the same wave lenght
the outcoming spectrum would be narrower. \\
We found a dependency of the equivalent width with the rotation of the gas cloud for all the models we study, this is shown in Figure ~\ref{figure:width}. As velocity increase also the equivalent width increase, it means that some photons escape with fewer scatterings than the static case but at the same time some photons escape with more scatterings.\\

% I dont understand this at all, hope Nscatts plot helps

@@

We also found that the equivalent width is not the same for differents angles of observation in particular as the angle increase the width also increase Figure ~\ref{fig:withvstheta}, this is related with the fact that photons escape easily (with less scatterings) in the $\hat{k}$ direction\\ 
Following the convention of Verhamme et al 2012 we define $\mu=cos(\theta)$, we can make a polynomial fit the $EW(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
%make comparison with Verhamme et al

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifODHOM.png}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifOD.png}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeedsHOM.png}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeeds.png}
  \label{figure:widthvstheta}\caption{Width of the lyman-alpha line for all the models. }
\end{figure*}

% fix this table is too big
\begin{table}
\begin{center}
\begin{tabular}{cc}\hline
Model & Fit\\
Central, $\tau=10^5, V=200\dfrac{km}{s}$ &$EW(\mu)=-59-1677\mu-17864\mu^{2}+84509\mu^{3}-149877\mu^{4}$\\
Central, $\tau=10^6, V=200\dfrac{km}{s}$ &$EW(\mu)=-1+53.8\mu-1080\mu^{2}+9644\mu^{3}-32264\mu^{4}$\\
Central, $\tau=10^7, V=200\dfrac{km}{s}$ & $EW(\mu)=0.011+0.9\mu-27\mu^{2}+359\mu^{3}-1791\mu^{4}$\\
Hom, $\tau=10^5, V=200\dfrac{km}{s}$ & $EW(\mu)=11.66-187.22\mu-54.58\mu^{2}+12932.5\mu^{3}-51882.9\mu^{4}$ \\
Hom, $\tau=10^6, V=200\dfrac{km}{s}$ & $EW(\mu)=-361.64+17158.92\mu-305268.4\mu^{2}+2413478\mu^{3}-7154649\mu^{4}$ \\
Hom, $\tau=10^7, V=200\dfrac{km}{s}$ & $EW(\mu)=-0.28+23.29\mu-721\mu^{2}+9912\mu^{3}-51074\mu^{4}$ \\
\hline
\end{tabular}
\caption{Fits for EW models} 
\label{table:fits}
\end{center}
\end{table}

@@

\section{Observational implications}
% taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.
